Market Expectations and Mangerial Turnover

### 2024-02-25 paper.qmd
some EDA in python

```{r}
library(readxl)
spells1 = read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
lspells2 = read_csv("raw_data/club_manager_histories_df.csv")
skimr::skim(spells_raw)
```

>>>>

```{python}
# Read the CSV files
spells1 = pd.read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
spells2 = pd.read_csv("raw_data/club_manager_histories_df.csv")

# Get a statistical summary of the data
summary1 = spells1.describe()
summary2 = spells2.describe()

print(summary1)
print(summary2)
```

```{python}
# Filter rows where the 'Finish' column is NaN
filtered_spells1 = spells1[spells1['Finish'].isna()]

# Create a frequency table of the 'contract_expiry' column
frequency_table = filtered_spells1['contract_expiry'].value_counts()

print(frequency_table)
```

```{python}
import numpy as np
def season_to_date(season):
    if pd.isnull(season) or '/' not in season:
        return np.nan

    parts = season.split('/')
    if int(parts[1]) < 80:
        year = '20' + parts[1]
    else:
        year = '19' + parts[1]

    date_str = '01/08/' + year
    return datetime.strptime(date_str, '%d/%m/%Y')

```{python}
# Apply the function only to rows where 'Date' is NaN
mask=spells1['Finish'].isna()
spells1.loc[mask, 'Finish'] = spells1.loc[mask,'contract_expiry'].apply(season_to_date)
#spells1[spells1['Finish'].isna()].value_counts()
spells1['Finish'].isna().value_counts()
```
